Chatbots and messaging platforms in the classroom: an analysis from the teacher's perspective

### 2023-01-09 edubots_surveys.Rnw
Update edubots_surveys.Rnw
Co-authored-by: Juan Julián Merelo Guervós <jjmerelo@gmail.com>

Despite its (arguably) successful implementation in different higher education
institutions, particularly on the fringes of educational activity rather than actual
student-teacher interaction, its implementation or deployment is not trivial.
Some authors, for instance \cite{sjostrom2018designing}, have proposed a
conceptual architecture for the adoption of teaching-oriented chatbots in higher
education.  This conceptual architecture is based on a systematic literature
review of previous studies examining the design of chatbots in higher
education, as well as making a content analysis of student emails and discussion
forum posts from four instances of a Java programming course.  The study outlined
several design considerations; among them, the authors emphasized the importance
of developing chatbots in platforms that students and educators are familiar
with and can easily access (i.e. Facebook Messenger), which was confirmed by
\cite{hobert2019you} and \cite{fernoagua2018intelligent}. In addition, \cite{sjostrom2018designing} argued that 
conceptualizing learners' questions could help designers integrate the
appropriate types of questions that chatbots should support for different
courses. Other authors, such as \cite{coronado2018cognitive}, have proposed agents that
store learning materials to be provided on demand to students, while \cite{crockett2017predicting} 
reported on tutoring systems that can
perform initial assessments of students' understanding and provide learning
materials to advance their understanding to the next level.

>>>>

Despite its (arguably) successful implementation in different higher education
institutions, particularly on the fringes of educational activity rather than actual
student-teacher interaction, its implementation or deployment is not trivial.
Some authors, for instance \cite{sjostrom2018designing}, have proposed a
conceptual architecture for the adoption of teaching-oriented chatbots in higher
education.  This conceptual architecture is based on a systematic literature
review of previous studies examining the design of chatbots in higher
education, as well as making a content analysis of student emails and discussion
forum posts from four instances of a Java programming course.  The study outlined
several design considerations; among them, the authors emphasized the importance
of developing chatbots in platforms that students and educators are familiar
with and can easily access (i.e. Facebook Messenger), which was confirmed by
\cite{hobert2019you} and \cite{fernoagua2018intelligent}. In addition, \cite{sjostrom2018designing} argued that 
conceptualizing learners' questions could help designers integrate the
appropriate types of questions that chatbots should support for different
courses. Other authors, such as \cite{coronado2018cognitive}, have proposed agents that
record learning materials to be provided on demand to students, while \cite{crockett2017predicting} 
reported on tutoring systems that can
perform initial assessments of students' understanding and provide learning
materials to advance their understanding to the next level.
